---
title: "Aquatic Vertebrate Biomass: Project for Productivity and Reproducibility 2025"
author: "Nicole Regimbal"
date: "2025-09-13"
output: pdf_document
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message= FALSE)
```

```{r loadlibs}
library(lme4)
library(glmmTMB)
```

# Introduction

This project assesses the effects of anthropogenic impacts on aquatic vertebrates in Mack Creek, Oregon.

The data is available as the **and_vertebrates** dataset from the *lterdatasampler* package in R.

This data assesses differences in biomass for 3 vertebrates compared between a anthropogenically disturbed (previously clear cut) and anthropogenically undisturbed (old growth) sites along the creek.

Previous research from [@kaylor2017] indicated that forest disturbances can affect vertebrate mass. This research inspired this research project, specifically looking at Coastal Cutthroat Trout, Coastal Giant Salamander and Cascade Torrent Salamander.

# Methods

## Field Sites

## Data Analaysis

```{r}
verts <- read.csv("../00_rawdata/and_vertebrates.csv")
```

# Results

```{r}
library(ggplot2)

```

ggsave(".04_manuscript/ms_figures/plot.png", a)

![figure caption](.ms/)

# Discussion

# References
